Inference methods comparison for the simplified Naomi model using the Kolmogorov-Smirnov test statistic

### 2025-08-05 src/naomi-simple_ks/ks.Rmd
Rerun of KS with correct MCMC samples

```{r}
rhats <- bayesplot::rhat(tmbstan$mcmc$stanfit)
ess_ratio <- bayesplot::neff_ratio(tmbstan$mcmc$stanfit)
niter <- 0.5 * 4 * tmbstan_details$niter / tmbstan_details$nthin
ess <- ess_ratio * niter

>>>>

```{r}
rhats <- bayesplot::rhat(tmbstan$mcmc$stanfit)
ess_ratio <- bayesplot::neff_ratio(tmbstan$mcmc$stanfit)
niter <- 0.5 * tmbstan_details$nchains * tmbstan_details$niter / tmbstan_details$nthin
ess <- ess_ratio * niter
